Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-09 Draft/process.tex
Validation of Alexander's changes

We now discuss the various approximations which are implemented in computer programs for the EW contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$.
Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
However, this set of contributions is not gauge invariant.
In order to ensure gauge invariance, an on-shell projection of
the incoming and outgoing W bosons should be performed.
While this can be done in the usual way for the time-like
outgoing W bosons, the treatment of the space-like W bosons
emitted from the incoming quarks requires some care.
Following Refs.~\cite{Kuss:1995yv,Accomando:2006hq} these W-boson lines can be split,
the W bosons entering the scattering process can be projected
on-shell, and the emission of the W bosons from the quarks can be
described by vector-boson luminosities.
Such an approximation is usually called effective vector-boson
approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

>>>>

We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
However, this set of contributions is not gauge invariant.
In order to ensure gauge invariance, an on-shell projection of
the incoming and outgoing W bosons should be performed.
While this can be done in the usual way for the time-like
outgoing W bosons, the treatment of the space-like W bosons
emitted from the incoming quarks requires some care.
Following Refs.~\cite{Kuss:1995yv,Accomando:2006hq} these W-boson lines can be split,
the W bosons entering the scattering process can be projected
on-shell, and the emission of the W bosons from the quarks can be
described by vector-boson luminosities.
Such an approximation is usually called effective vector-boson
approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
